%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

% Command for printing skill overview bubbles
%\newcommand\skills{ 
%~
%	\smartdiagram[bubble diagram]{
%        \textbf{Data}\\\textbf{Engineering},
%        \textbf{Full Stack}\\\textbf{Dev},
%        \textbf{~~~~~~~~OOP~~~~~~~~~},
%        \textbf{~~~~~~Machine~~~~~~}\\\textbf{~~Learning~~},
%        \textbf{~~~~~DevOps~~~~~}
%    }
%}

% Command for printing skill overview bubbles
\newcommand\skills{ 
An experienced analyst focusing on operations research, data analytics, statistics, and machine learning. Skilled at taking data, transforming it into business insights, and presenting it to all levels of leadership. Creating automation solutions to drive operational efficiency.
}


% Programming skill bars
\programming{
	{Python, SAS, VBA, R, JMP, Matlab}, 
	{REST, SOAP, JSON},
	{Selenium, pywin32},
	{SQL Server, PostgreSQL, SQLite},
	{Git, Azure DevOps, GitHub},
	{Markdown, \LaTeX}
}


% Other Software
\software{
	{Excel, Word, Outlook, PowerPoint, SharePoint},
	{QNXT, Trapeze}
}

% Projects text
\education{
\textbf{MS, Mathematics}\\
Portland State University \\
2010 - 2012 | Portland, OR\\
Focus: Numerical Analysis, Mathematical Analysis, Differential Equations, Graph Theory\\
Research Paper: \textit{“Numerical methods for ordinary differential equations and their implementation in MATLAB”}

\textbf{BA, Economics}\\
Minor: Mathematics\\
Focus: Development, Mathematical Economics, Econometrics, Statistics \\
Portland State university \\
2008 - 2010 | Portland, OR
}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{C. Bray Ellison} % Your name
\cvjobtitle{Data Analyst} % Job
% title/career

\cvnumberphone{971-533-4161} % Phone number
\cvsite{} % Personal website
\cvmail{brayellison@gmail.com} % Email address
\cvlinkedin{/in/cbrayellison}
\cvgithub{brayellison}

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
\twentyitem
    	{May 2017 -}{Present}
        {Operations Analyst 3}
        {\href{https://www.virginiapremier.com/}{Virginia Premier}}
        {}
        {\begin{itemize}
			\item Automated the entry of health risk assessments clearing out a four-month backlog. This is estimated to have saved over 13k productive hours and replaced a team entering them manually.
			\item Updated systems integration testing utilizing Selenium, generating over 6k test cases where there was normally about 50. This led to over 99\% of Transportation claims properly adjudicating.
			\item Brought Anaconda/Python to Virginia Premier and became the SME for Python at the company. Established Anaconda Working Group to have Python training disseminated to all analysts at the company. 
			\item Was requested by the COO to participate in the Operational Excellence initiative, helping to overhaul benefits configuration in our claims adjudication system for prior authorization requirements and accumulators

        \end{itemize}}
        \\
	\twentyitem
    	{Feb. 2015 -}{Mar. 2017}
        {AVP, Operations Research Analyst II}
        {\href{https://www.bankofamerica.com/}{Bank of America}}
        {}
        {
        {\begin{itemize}
			\item Role previously performed by various partners, but consolidated into a single role, creating forecasts for seven out of eight of the functions for existing Customer Credit.
			\item Performed research and presented findings to broader Home Loans Fulfillment Forecasting, Reporting, Analytics and Capacity Planning organization.
			\item Forecasts showed downward trend in work for the department. This led to the transition of over 50 associates to other roles within the bank over a year and a half long period, leading to significant cost savings due to a reduction in force while preserving jobs.
    	\end{itemize}}
        }
    \\   
    \twentyitem
   		{Dec. 2013 -}{Feb. 2015}
        {Credit Quality Analyst}
        {\href{https://www.bankofamerica.com/}{Bank of America}}
        {}
        {
        {\begin{itemize}
			\item Was one of the first employees to join this team, quickly became an SME for the role and helped create a standardization of practices.
			\item Performed ad-hoc analyses leading to policies that increased outbound contact percentages by 10\%.
			\item Created employee metrics which led to lower overall variance in performance.
			\item Ran training sessions for new hires and current associates, coached teammates and performed side by sides to ensure compliance with policy and processes. 
 	   \end{itemize}}
        }
     \\
     \twentyitem
   		{Feb. 2013 -}{Dec. 2013}
        {Home Services Specialist I}
        {\href{https://www.bankofamerica.com/}{Bank of America}}
        {}
        {
        \begin{itemize}
        	\item Performance was recognized by becoming dedicated loan processor for highest grossing mortgage loan officer on west coast.
        	\item Process loan applications for non-conforming, conforming and conforming high-balance first mortgage and combo loan products. Perform initial underwriting of loan applications. Assist coworkers and new hires with questions regarding policies and systems.
	    \end{itemize}
    	}
    \\
	\twentyitem
		{Aug. 2012 -}{Feb. 2013}
		{MLO-Loan Closer}
		{\href{https://www.bankofamerica.com/}{Bank of America}}
		{}
		{
		\begin{itemize}
			\item Create final documents for first mortgage purchases and refinance. Ensure mortgage documentation follows federal and company guidelines. Maintain contact with borrowers to explain steps in closing. Train new hires in closing process.
		\end{itemize}
		}
        
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 RESEARCH
%----------------------------------------------------------------------------------------
\section{Research Interests}
%\begin{twenty}
%	\twentyitem
%    	{2015 - 2017}
%		{}
%        {MSc. Candidate, Graduate Research Assistant}
%        {\href{http://www.uoguelph.ca/}{University of Guelph}}
%        {}
%        {
%       	\textbf{Thesis}: Data Integration from Multiple Historical Sources to Study Canadian Casualties of WWI
%        {\begin{itemize}
%        \item Proposed a stepwise deterministic method to integrate datasets without labeled data. The method performs comparably with a method that incorporates a Support Vector Machine
%        \item Prepared a longitudinal dataset to enable comprehensive analyses about WWI Canadian society and military, seeding further research
%        \item \textbf{Tools}: R, Python, scikit-learn, pandas \vspace{2mm}
%		\end{itemize}}
%        }
%\end{twenty}
Geospatial unsupervised learning, time-series forecasting using RNNs/LSTMs, iterative hyperplane fitting.

%\section{Publications}
%L. Antonie, H. Gadgil, G. Grewal, and K. Inwood, “Historical Data Integration - A Study of WWI Canadian Soldiers,” in 2016 IEEE 16th International Conference on Data Mining Workshops (ICDMW), pp. 186-193, IEEE, 2016. \vspace{2mm}

\end{document} 
